Comparison of dimensionality reduction schemes for parallel global optimization algorithms

### 2018-05-10 2018/YSC/ysc_abstract.tex
YSC: add abstract

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%%%%%
\usepackage{eqnarray,amsmath}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\setlength{\textfloatsep}{4pt plus 1.0pt minus 1.5pt}
\setlength{\floatsep}{4pt plus 1.0pt minus 1.5pt}

\begin{document}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
%
\title{Comparison of dimensionality reduction schemes for parallel global optimization
algorithms 
\thanks{The study was supported by the Russian Science Foundation, project No 16-11-
10150}}
%
\titlerunning{Dimension reduction schemes in parallel GO}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Konstantin Barkalov \and
Vladislav Sovrasov \and
Ilya Lebedev}
%
\authorrunning{K. Barkalov et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
\email{konstantin.barkalov@itmm.unn.ru}\\
\email{sovrasov.vlad@gmail.com}\\
\email{ilya.lebedev@itmm.unn.ru}\\
\url{http://hpc-education.unn.ru/}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
This work considers a parallel algorithms for solving multi-extremal optimization problems.
Algorithms are developed within the framework of the information-statistical approach and
implemented in a parallel solver Globalizer. The optimization problem is solved by reducing
the multidimensional problem to a set of joint one-dimensional problems that are solved in
parallel. Five types of Peano-type space-filling curves are employed to reduce dimension. The
results of computational experiments carried out on several hundred test problems are discussed.

\keywords{Global optimization \and  Dimension reduction \and Parallel algorithms  \and
Multidimensional multiextremal optimization  \and Global search algorithms  \and Parallel
computations }
\end{abstract}

%------------------------------------------------------------------------------
\section{Introduction}\label{sec:intro}
%\begin{Russian}

@@

\bibitem{stronginGergelBarkalovParGO}
\newblock R. G. Strongin, V. P. Gergel, V. A. Grishagin and K. A. Barkalov,
\newblock \emph{Parallel Computations for Global Optimization Problems},
\newblock Moscow State University, Moscow (2013) (In Russian)

\bibitem{strSergGO}%5 (MR1797058) [10.1007/978-1-4615-4677-1]
\newblock R. G. Strongin and Y. D. Sergeyev,
\newblock \emph{Global Optimization with Non-convex Constraints. Sequential and Parallel
Algorithms},
\newblock Kluwer Academic Publishers, Dordrecht (2000, 2nd ed. 2013, 3rd ed. 2014)

\bibitem{zilinskTornGO}% (MR1100586) [10.1007/3-540-50871-6]
\newblock A. T\"orn and A. \v Zilinskas,
\newblock \emph{Global Optimization},
\newblock Springer, (1989)

@@

\bibitem{zhigljavskyRandGO}% (MR1187048) [10.1007/978-94-011-3436-1]
\newblock A. A. Zhigljavsky,
\newblock \emph{Theory of Global Random Search},
\newblock Kluwer Academic Publishers, Dordrecht (1991)

\bibitem{Strongin1991}
Strongin, R.G.: \emph{Parallel multi-extremal optimization using a set of evolvents}. Comp. Math.
Math. Phys. \textbf{31(8)}, 37--46 (1991)

@@

\bibitem{Gaviano2003}
Gaviano, M., Kvasov, D.E, Lera, D., and Sergeyev, Ya.D.: \emph{Software for generation of classes
of test functions with known local and global minima for global optimization.} ACM
Transactions on Mathematical Software \textbf{29(4)}, 469--480 (2003)

\bibitem{grishaginClass}
Grishagin, V.A.: \emph{Operating Characteristics of Some Global Search Algorithms.} Problems of
Statistical Optimization \textbf{7}, 198--206 (1978) (In Russian)

@@

\end{thebibliography}
\end{document}

>>>>

% easychair.tex,v 3.1 2011/12/30
%
% Select appropriate paper format in your document class as
% instructed by your conference organizers. Only withtimes
% and notimes can be used in proceedings created by EasyChair
%
% The available formats are 'letterpaper' and 'a4paper' with
% the former being the default if omitted as in the example
% below.
%
\documentclass[procedia]{easychair}
%\documentclass[debug]{easychair}
%\documentclass[verbose]{easychair}
%\documentclass[notimes]{easychair}
%\documentclass[withtimes]{easychair}
%\documentclass[a4paper]{easychair}
%\documentclass[letterpaper]{easychair}

% This provides the \BibTeX macro
\usepackage{doc}
\usepackage{makeidx}

% In order to save space or manage large tables or figures in a
% landcape-like text, you can use the rotating and pdflscape
% packages. Uncomment the desired from the below.
%
% \usepackage{rotating}
% \usepackage{pdflscape}

% If you plan on including some algorithm specification, we recommend
% the below package. Read more details on the custom options of the
% package documentation.
%
% \usepackage{algorithm2e}

\def\procediaConference{99th Conference on Topics of
  Superb Significance (COOL 2014)}

%\makeindex

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Comparison of dimensionality reduction schemes for parallel global optimization
algorithms}

% \titlerunning{} has to be set to either the main title or its shorter
% version for the running heads. When processed by
% EasyChair, this command is mandatory: a document without \titlerunning
% will be rejected by EasyChair

\titlerunning{Dimension reduction schemes in parallel GO}

% Authors are joined by \and. Their affiliations are given by \inst, which indexes into the list
% defined using \institute
%
\author {
Vladislav Sovrasov \and
Ilya Lebedev
}

% Institutes for affiliations are also joined by \and,
\institute  {
  Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
  \email{sovrasov.vlad@gmail.com}\\
  \email{ilya.lebedev@itmm.unn.ru}\\
}
%  \authorrunning{} has to be set for the shorter version of the authors' names;
% otherwise a warning will be rendered in the running heads. When processed by
% EasyChair, this command is mandatory: a document without \authorrunning
% will be rejected by EasyChair

\authorrunning{Sovrasov V., Lebedev I.}

\begin{document}

\maketitle

\keywords{Global optimization, Dimension reduction, Parallel algorithms,
Multidimensional multiextremal optimization, Global search algorithms}

\begin{abstract}
This work considers a parallel algorithms for solving multi-extremal optimization problems.
Algorithms are developed within the framework of the information-statistical approach and
implemented in a parallel solver Globalizer. The optimization problem is solved by reducing
the multidimensional problem to a set of joint one-dimensional problems that are solved in
parallel. Five types of Peano-type space-filling curves are employed to reduce dimension. The
results of computational experiments carried out on several hundred test problems are discussed.
\end{abstract}

%\setcounter{tocdepth}{2}
%{\small
%\tableofcontents}

%\section{To mention}
%
%Processing in EasyChair - number of pages.
%
%Examples of how EasyChair processes papers. Caveats (replacement of EC
%class, errors).

%------------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}

@@

@@

@@

@@

\end{thebibliography}

%------------------------------------------------------------------------------
\end{document}

% EOF
